Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-26 paper/main.tex
some updates

\documentclass[runningheads]{llncs}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{relsize}
\usepackage{amsmath,amssymb}
%\usepackage[square,numbers,sort&compress]{natbib}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape,adjustbox}
\usepackage{multirow}

@@

\subsubsection{CEGO.}
We use the implementation of GECO provided by the
authors.\footnote{\url{https://cran.r-project.org/package=CEGO}} %
Although it is never stated in the original paper, the implementation of CEGO
generates a set of initial solutions of size $\minit=10$ by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the true fitness function
and the result is used to build the initial surrogate
model.% \citet{ZaeStoBar2014:ppsn} uses \minit=10
Following the authors of
CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use a GA to optimize
the surrogate models with population size of 20, crossover rate of 0.5,
mutation rate of $1/n$, tournament selection of size 2 with probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements) and
cycle crossover for permutations. To generate each new solution, CEGO runs the
GA using the model as a surrogate of the true fitness function.  The authors of
CEGO used a budget of $10^4$ surrogate-model evaluations for each run of the
GA. However, with such a setting, a single run of CEGO with a budget of $\FEmax=400$
true fitness evaluations requires \emph{more than a week} of computation time,
which was infeasible for our study. Hence, we set the budget of the GA to
$10^3$. Although a higher GA budget could improve the results of CEGO reported
here, our results are similar (and sometimes better) than the ones reported in
the original papers~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn} due to
running CEGO with $\FEmax=400$ instead of $\FEmax=200$. In fact, we found that the
increase in runtime caused by doubling $\FEmax$ is much smaller than by increasing
the GA budget by a factor of $10$. Nevertheless, we caution that choosing a
different trade-off may lead to different conclusions and more work is needed
to understand CEGO parameters.

\subsubsection{Other}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance. We plan to extend our analysis of UMM to other
distance measures and to the dynamic selection of distance
measures~\citep{ZaeStoBar2014:ppsn}. In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
\textcolor{red}{hundreds? thousands?} of solutions, thus, the budget considered
here for the black-box context is extremely limited.

We implemented UMM in Python 3. The parameter settings that we use are...

\manuel{Computing system details: MANUEL}{%
  All experiments were run on Intel Xeon ``Ivybridge'' E5-2650v2 CPUs at 2.60\,GHz, 64\,GB RAM
  running CentOS Linux release 7.4.1708 (Core).  }

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{relsize}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape,adjustbox}
\usepackage{multirow}

@@

\subsubsection{CEGO.}
We use the implementation of GECO provided by the
authors.\footnote{\url{https://cran.r-project.org/package=CEGO}} %
Although it is never stated in the original paper, the implementation of CEGO
generates a set of initial solutions of size $\minit=10$ by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the true fitness function
and the result is used to build the initial surrogate
model. % \citet{ZaeStoBar2014:ppsn} uses \minit=10
Following the authors of
CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use a GA to optimize
the surrogate models with population size of 20, crossover rate of 0.5,
mutation rate of $1/n$, tournament selection of size 2 with probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements) and
cycle crossover for permutations. To generate each new solution, CEGO runs the
GA using the model as a surrogate of the true fitness function.  The authors of
CEGO used a budget of $10^4$ surrogate-model evaluations for each run of the
GA. However, with such a setting, a single run of CEGO with a budget of $\FEmax=400$
true fitness evaluations requires \emph{more than a week} of computation time,
which was infeasible for our study. Hence, we set the budget of the GA to
$10^3$. Although a higher GA budget could improve the results of CEGO reported
here, our results are similar (and sometimes better) than the ones reported in
the original papers~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn} due to
running CEGO with $\FEmax=400$ instead of $\FEmax=200$. In fact, we found that the
increase in runtime caused by doubling $\FEmax$ is much smaller than by increasing
the GA budget by a factor of $10$. Nevertheless, we caution that choosing a
different trade-off may lead to different conclusions and more work is needed
to understand CEGO parameters.

\subsubsection{UMM}. UMM uses the same budget of evaluation ($\FEmax$) as CEGO
and initially samples $\minit=10$ solutions uniformly. The other two parameters
of UMM are $r_1$ and $r_2$, which determine the balance between exploration and
exploitation. In the experimental section we will study their impact. We
implemented UMM using Python 3.

\subsubsection{Other}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance.  We plan to extend UMM to other distance measures
and to the dynamic selection of distance measures~\citep{ZaeStoBar2014:ppsn}.
In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
\textcolor{red}{hundreds? thousands?} of solutions, thus, the budget considered
here for the black-box context is extremely limited.

@@

\subsubsection{Computing environment.}
All experiments were run on Intel Xeon ``Ivybridge'' E5-2650v2 CPUs at
2.60\,GHz, 64\,GB RAM running CentOS Linux release 7.4.1708 (Core).
\MANUEL{This may need updating since you ran some experiments? didn't you?}
